### 2016-11-08 paper3.tex
Fixed fancy header for chapters and abstracts
Shuffled and resized figures

\setcounter{pageFix}{\value{page}}
\begin{abstract}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure*}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=0.63\textwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

\subsection{Redshift zero properties}

@@

\subsection{Stellar Mass Runaway}
As can be seen in Fig.~\ref{SMHMR}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties of the using dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image}.

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

Fig.~\ref{massloading_halo} suggests exactly that.  The mass loadings appear
roughly constant, at $\eta\sim10$ for most of the mass-range for both
populations, but begin to fall at essentially the same mass, at what appears to
be the same rate.  An even tighter relation is seen in
Fig.~\ref{massloading_central}, when the relation between the central baryon
mass, rather than just the halo mass, is examined. It appears that for the
$\eta-M_{\rm halo}$ and $\eta-M_{\rm central}$ relation, a broken power-law fit, as
defined below, describes both the regulated and unregulated population.
\begin{equation}
    \eta = 
    \begin{cases}
        \alpha M^\beta  & \quad \text{if } M > M_0 \\
        (\alpha M_0^{\beta-\gamma}) M^\gamma & \quad \text{if } M < M_0 \\
    \end{cases}
    \label{outflow_scaling}
\end{equation}

@@

The temperature of the outflows also shows an interesting trend as a function of
halo mass.  Fig.~\ref{coldmassloading} shows that as halo mass increases, the
mass loading of outflows with cold gas monotonically decreases, while the
loading of hot gas is convex, peaking at $M_{\rm halo} =
\operatorname{2-5}\times10^{11}\;\Msun$, and then rapidly falling as halo mass
increases.  We define cold gas as having $T<10^5\K$.  We choose this as a cutoff
point as it lies near the peak of the cooling curve, where we would expect, as
\citet{Woods2014} showed, very little gas to be found.  If we think in terms of
virial temperature, this makes sense.  At low $T_{\rm vir}$, gas around $10^5\K$ is
buoyant, and will be driven out of the disc.  The halo itself is smaller, with a
shallower potential well, thus making it easier for the same amount of feedback
energy to eject a larger amount of entrained gas.  As the halo mass grows,
eventually only the hottest gas is able to escape, and only if it is not weighed
down by too much entrained material.  Eventually, this effect means that the
total mass loading begins to drop significantly.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/massloading_escape.eps}
    \caption[Mass loading vs. escape velocity of disc]{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}

@@

\subsection{Redshift zero properties}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=0.63\textwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

@@

\subsection{Stellar Mass Runaway}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
As can be seen in Fig.~\ref{SMHMR}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties of the using dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image}.

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

Fig.~\ref{massloading_halo} suggests exactly that.  The mass loadings appear
roughly constant, at $\eta\sim10$ for most of the mass-range for both
populations, but begin to fall at essentially the same mass, at what appears to
be the same rate.  An even tighter relation is seen in
Fig.~\ref{massloading_central}, when the relation between the central baryon
mass, rather than just the halo mass, is examined. It appears that for the
$\eta-M_{\rm halo}$ and $\eta-M_{\rm central}$ relation, a broken power-law fit, as
defined below, describes both the regulated and unregulated population.
\begin{equation}
    \eta = 
    \begin{cases}
        \alpha M^\beta  & \quad \text{if } M > M_0 \\
        (\alpha M_0^{\beta-\gamma}) M^\gamma & \quad \text{if } M < M_0 \\
    \end{cases}
    \label{outflow_scaling}
\end{equation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}

@@

The temperature of the outflows also shows an interesting trend as a function of
halo mass.  Fig.~\ref{coldmassloading} shows that as halo mass increases, the
mass loading of outflows with cold gas monotonically decreases, while the
loading of hot gas is convex, peaking at $M_{\rm halo} =
\operatorname{2-5}\times10^{11}\;\Msun$, and then rapidly falling as halo mass
increases.  We define cold gas as having $T<10^5\K$.  We choose this as a cutoff
point as it lies near the peak of the cooling curve, where we would expect, as
\citet{Woods2014} showed, very little gas to be found.  If we think in terms of
virial temperature, this makes sense.  At low $T_{\rm vir}$, gas around $10^5\K$ is
buoyant, and will be driven out of the disc.  The halo itself is smaller, with a
shallower potential well, thus making it easier for the same amount of feedback
energy to eject a larger amount of entrained gas.  As the halo mass grows,
eventually only the hottest gas is able to escape, and only if it is not weighed
down by too much entrained material.  Eventually, this effect means that the
total mass loading begins to drop significantly.
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_escape.eps}
    \caption[Mass loading vs. escape velocity of disc]{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}

@@

### 2016-11-08 paper4.tex
Fixed page numbering
Fixed figure sizes
Fixed fancy header for chapters and abstracts
Fixed bibliography issue
Shuffled and resized figures

\begin{abstract}
        \addcontentsline{toc}{section}{Abstract}
    Recent analysis \citep{McGaugh2016} of the SPARC galaxy sample found a
    surprisingly tight relation between the radial acceleration inferred from
    the rotation curves, and the acceleration due to the baryonic components of
    the disc.  It has been suggested that this relation may be evidence for new
    physics, beyond $\Lambda CDM$.  In this letter we show that the 18
    galaxies from the MUGS2 match the SPARC acceleration relation. These
    cosmological simulations of star forming, rotationally supported discs were
    simulated with a {\sc WMAP3} $\Lambda CDM$ cosmology, and match the SPARC
    acceleration relation with less scatter than the observational data.  These
    results show that this acceleration law is a consequence of
    dissipative collapse of baryons, rather than being evidence for exotic
    dark-sector physics or new dynamical laws.
\end{abstract}

@@

\section{The MUGS2 Sample}
The McMaster Unbiased Galaxy Simulations 2 (MUGS2) sample is an unbiased,
statistically representative set of 18 cosmological zoom-in simulations of $L*$
disc galaxies.  These galaxies were simulated in a {\sc WMAP3} $\Lambda CDM$
cosmology, with parameters $H_0 = 73\kms \Mpc^{-1}$, $\Omega_M=0.24$,
$\Omega_{bar}=0.04$, $\Omega_\Lambda=0.76$, and $\sigma_8=0.76$.  The MUGS2
$z=0$ halo masses range from $3.7\times10^{11}\Msun$ to $2.2\times10^{12}\Msun$,
with disc masses ranging from $1.8\times10^{10}\Msun$ to
$2.7\times10^{11}\Msun$.  For more details on the creation of the MUGS2 initial
conditions, see the original MUGS paper, \citet{Stinson2010}.  For more
information on the simulations themselves, see \citet{Keller2015,Keller2016}.

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/SPARC_plot.eps}
    \caption[Total acceleration vs. baryonic acceleration in MUGS2]{Total
    acceleration ($g_{obs}$) vs acceleration due to baryons ($g_{bar}$) from
    1800 data points in the $z=0$ MUGS2 sample, shown in the blue 2-dimensional
    histogram.  The dotted black curve shows the 1:1 relation expected if the
    acceleration was due to baryons alone (without dark matter), while the solid
    line shows the relation presented in \citet{McGaugh2016}.  A Gaussian
    distribution fitted to these residuals finds a variance of $\sigma=0.05$
    dex, significantly lower than the 0.11 dex found by \citet{McGaugh2016}.}
    \label{SPARC_plot}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/redshift_evolution.eps}
    \caption[Redshift evolution of acceleration relation]{The  simulated
    $g_{obs}-g_{bar}$ relation is not constant with redshift.  As this figure
    shows, at higher redshift the low $g_{bar}$ slope is much shallower than at
    $z=0$.  This shows that for high redshift galaxies, their discs can be
    depleted of baryons compared with $z=0$.  We have focused on the low
    $g_{bar}$ end of the relation here, where the changes are most significant.}
    \label{redshift_evolution}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/FB_effects.eps}
    \caption[Feedback effects on acceleration relation]{The evolution seen in
    figure~\ref{redshift_evolution} is primarily driven by feedback.  This can
    be seen when looking at the same galaxy with and without feedback.  Without
    feedback, the baryon fraction within the disc increases slightly from $z=0$
    to $z=2$, but still roughly follows the SPARC relation.  At $z=2$, strong
    outflows in the galaxy expel most of the baryons from the disc, flattening
    the acceleration relation.  This effect is sensitive to the frequent
    merger-driven starbursts at high redshift, which can drive bursty outflows.}
    \label{FB_effects}
\end{figure}
\section{Results}
\subsection{z=0 Acceleration Relation}
The MUGS2 sample gives us 1800 acceleration data points, just over 2/3 the
sample size of \citet{McGaugh2016}. We show in figure~\ref{SPARC_plot} the
$g_{obs}-g_{bar}$ relation for the MUGS2 sample, compared both to the pure
baryonic acceleration and the SPARC acceleration relation.  It is clear these
simulated galaxies follow the \citet{McGaugh2016} relation {\it extremely} well.
As can be seen from the inset residual distribution, our simulated galaxies
follow the SPARC relation even more tightly than the actual observational data.
The scatter we do see, with $\sigma=0.05$ dex, is consistent with the
\citet{McGaugh2016} estimates.  They decomposed their scatter of $0.11$
dex into different sources, and when all of the observational uncertainties are
removed, the remaining intrinsic scatter gives a variance of $\sigma=0.06$ dex,
very close to the value we find here.  A reduced $\chi^2$ statistic of the SPARC
relation fit to the $z=0$ MUGS2 data finds a very good fit, with $\chi^2_\nu =
1.25$.  These simulation data are fit by equation~\ref{g_fit} at least as well
as the original SPARC data.

\subsection{Feedback \& the Evolution of the Acceleration Relation}
If the SPARC acceleration law is in fact due to new physics, it would be
surprising if the law did not hold at all redshifts.  This would not be the case
if the relation was simply a consequence of galaxy evolution.  In
figure~\ref{redshift_evolution} we show that the acceleration relation in the MUGS2
sample actually shows significant redshift dependence, and only settles to
the equation~\ref{g_fit} relation near z=0.  For these data points, we scaled
the thickness of the annuli by the cosmic scale factor $a$, so that $\delta r =
300a\pc$.  We use this scaling to ensure we are sampling primarily from the
stellar disc, and not well beyond it.  Omitting this scaling has little effect
on these results, save for extending the points to very low values of $g_{bar}$
and removing points from the high $g_{bar}$ end.  This evolution is a
consequence of the huge impact that stellar feedback has on galaxies at
$z\sim2$.  \citet{Keller2015} showed that SNe drive hot outflows from high
redshift galaxies with mass loadings of $\dot M_{out}/\dot M_* \sim 10$.  This
leads to discs at high redshift with baryon fractions depleted relative to those at
low redshift.  This feedback effect is clear when a single galaxy, g1536, is
compared to the same galaxy simulated without SNe feedback.  As
figure~\ref{FB_effects} shows, the redshift trend is nearly nonexistent without SNe
feedback.  Even at $z=2$, the galaxy without feedback falls within the scatter
of the SPARC acceleration law, and within the scatter of the $z=0$ MUGS2
relation.  This tells us that we need not invoke feedback processes to explain
the SPARC acceleration law.  Simple dissipational collapse of gas is sufficient
to produce a similar relation.  The evolution we see as a function of redshift
is therefore dominated primarily by the stronger effect of feedback at higher
redshift.

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}
    Recent analysis \citep{McGaugh2016} of the SPARC galaxy sample found a
    surprisingly tight relation between the radial acceleration inferred from
    the rotation curves, and the acceleration due to the baryonic components of
    the disc.  It has been suggested that this relation may be evidence for new
    physics, beyond $\Lambda CDM$.  In this letter we show that the 18
    galaxies from the MUGS2 match the SPARC acceleration relation. These
    cosmological simulations of star forming, rotationally supported discs were
    simulated with a {\sc WMAP3} $\Lambda CDM$ cosmology, and match the SPARC
    acceleration relation with less scatter than the observational data.  These
    results show that this acceleration law is a consequence of
    dissipative collapse of baryons, rather than being evidence for exotic
    dark-sector physics or new dynamical laws.
\end{abstract}

@@

\section{The MUGS2 Sample}
The McMaster Unbiased Galaxy Simulations 2 (MUGS2) sample is an unbiased,
statistically representative set of 18 cosmological zoom-in simulations of $L*$
disc galaxies.  These galaxies were simulated in a {\sc WMAP3} $\Lambda CDM$
cosmology, with parameters $H_0 = 73\kms \Mpc^{-1}$, $\Omega_M=0.24$,
$\Omega_{bar}=0.04$, $\Omega_\Lambda=0.76$, and $\sigma_8=0.76$.  The MUGS2
$z=0$ halo masses range from $3.7\times10^{11}\Msun$ to $2.2\times10^{12}\Msun$,
with disc masses ranging from $1.8\times10^{10}\Msun$ to
$2.7\times10^{11}\Msun$.  For more details on the creation of the MUGS2 initial
conditions, see the original MUGS paper, \citet{Stinson2010}.  For more
information on the simulations themselves, see \citet{Keller2015,Keller2016a}.

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures4/SPARC_plot.eps}
    \caption[Total acceleration vs. baryonic acceleration in MUGS2]{Total
    acceleration ($g_{obs}$) vs acceleration due to baryons ($g_{bar}$) from
    1800 data points in the $z=0$ MUGS2 sample, shown in the blue 2-dimensional
    histogram.  The dotted black curve shows the 1:1 relation expected if the
    acceleration was due to baryons alone (without dark matter), while the solid
    line shows the relation presented in \citet{McGaugh2016}.  A Gaussian
    distribution fitted to these residuals finds a variance of $\sigma=0.05$
    dex, significantly lower than the 0.11 dex found by \citet{McGaugh2016}.}
    \label{SPARC_plot}
\end{figure}
\section{Results}
\subsection{z=0 Acceleration Relation}
The MUGS2 sample gives us 1800 acceleration data points, just over 2/3 the
sample size of \citet{McGaugh2016}. We show in figure~\ref{SPARC_plot} the
$g_{obs}-g_{bar}$ relation for the MUGS2 sample, compared both to the pure
baryonic acceleration and the SPARC acceleration relation.  It is clear these
simulated galaxies follow the \citet{McGaugh2016} relation {\it extremely} well.
As can be seen from the inset residual distribution, our simulated galaxies
follow the SPARC relation even more tightly than the actual observational data.
The scatter we do see, with $\sigma=0.05$ dex, is consistent with the
\citet{McGaugh2016} estimates.  They decomposed their scatter of $0.11$
dex into different sources, and when all of the observational uncertainties are
removed, the remaining intrinsic scatter gives a variance of $\sigma=0.06$ dex,
very close to the value we find here.  A reduced $\chi^2$ statistic of the SPARC
relation fit to the $z=0$ MUGS2 data finds a very good fit, with $\chi^2_\nu =
1.25$.  These simulation data are fit by equation~\ref{g_fit} at least as well
as the original SPARC data.

\subsection{Feedback \& the Evolution of the Acceleration Relation}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures4/redshift_evolution.eps}
    \caption[Redshift evolution of acceleration relation]{The  simulated
    $g_{obs}-g_{bar}$ relation is not constant with redshift.  As this figure
    shows, at higher redshift the low $g_{bar}$ slope is much shallower than at
    $z=0$.  This shows that for high redshift galaxies, their discs can be
    depleted of baryons compared with $z=0$.  We have focused on the low
    $g_{bar}$ end of the relation here, where the changes are most significant.}
    \label{redshift_evolution}
\end{figure}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures4/FB_effects.eps}
    \caption[Feedback effects on acceleration relation]{The evolution seen in
    figure~\ref{redshift_evolution} is primarily driven by feedback.  This can
    be seen when looking at the same galaxy with and without feedback.  Without
    feedback, the baryon fraction within the disc increases slightly from $z=0$
    to $z=2$, but still roughly follows the SPARC relation.  At $z=2$, strong
    outflows in the galaxy expel most of the baryons from the disc, flattening
    the acceleration relation.  This effect is sensitive to the frequent
    merger-driven starbursts at high redshift, which can drive bursty outflows.}
    \label{FB_effects}
\end{figure}
If the SPARC acceleration law is in fact due to new physics, it would be
surprising if the law did not hold at all redshifts.  This would not be the case
if the relation was simply a consequence of galaxy evolution.  In
figure~\ref{redshift_evolution} we show that the acceleration relation in the MUGS2
sample actually shows significant redshift dependence, and only settles to
the equation~\ref{g_fit} relation near z=0.  For these data points, we scaled
the thickness of the annuli by the cosmic scale factor $a$, so that $\delta r =
300a\pc$.  We use this scaling to ensure we are sampling primarily from the
stellar disc, and not well beyond it.  Omitting this scaling has little effect
on these results, save for extending the points to very low values of $g_{bar}$
and removing points from the high $g_{bar}$ end.  This evolution is a
consequence of the huge impact that stellar feedback has on galaxies at
$z\sim2$.  \citet{Keller2015} showed that SNe drive hot outflows from high
redshift galaxies with mass loadings of $\dot M_{out}/\dot M_* \sim 10$.  This
leads to discs at high redshift with baryon fractions depleted relative to those at
low redshift.  This feedback effect is clear when a single galaxy, g1536, is
compared to the same galaxy simulated without SNe feedback.  As
figure~\ref{FB_effects} shows, the redshift trend is nearly nonexistent without SNe
feedback.  Even at $z=2$, the galaxy without feedback falls within the scatter
of the SPARC acceleration law, and within the scatter of the $z=0$ MUGS2
relation.  This tells us that we need not invoke feedback processes to explain
the SPARC acceleration law.  Simple dissipational collapse of gas is sufficient
to produce a similar relation.  The evolution we see as a function of redshift
is therefore dominated primarily by the stronger effect of feedback at higher
redshift.
